animbook: An R Package for Visualize \ldots{}

### 2023-09-11 animbook-journal.Rmd
add new section
add content to the first section

---
title: "animbook: An R Package for Visualize ..."
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

@@

  The structure of this paper will consist of four main section. The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve. Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage. The third section is visualization and interaction design, designing the visuals and refining the tools. In the last section, package design, develop the structure of the packages and how to implement the final visualize design into the R package. The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.

# Domain problem and data characterization

@@

>>>>

---
title: "animbook: An R Package for Visualize ..."
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib

@@

  The structure of this paper will consist of four main section. The first section is domain problem and data characterization, identifying the problems the visualization tools try to solve. Secondly, the operation and data type abstraction, the description of operations, and the types of data required for the next stage. The third section is visualization and interaction design, designing the visuals and refining the tools. In the forth section, package design, develop the structure of the packages and how to implement the final visualize design into the R package. Lastly, the package usage. The checking of the threat and validating of that threat will be carried out throughout the entire process of designing the animbook package.

# Problem and data characterization

To look for the flow between group, one of the most common tools we look at is sankey chart. It represent the movement of the values from one set to another. However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary. To present more information, color could be used to represent the demographic of the group. What if the information that are interesting lies in the times domain, how could the plot captured that information?

!!general sankey plot and sankey with color

The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer. Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time. The animation in this tools has created a new way for people to analyse and visualize the trend.

!!read effectiveness of animation in trend visualization, then add more information to above paragraph

The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world. This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.

@@

# Package Usage

### 2023-09-11 animbook-journal.tex
add content to the first section

@@

\bibliography{RJreferences.bib}

>>>>

To look for the flow between group, one of the most common tools we look at is sankey chart. It represent the movement of the values from one set to another. However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary. To present more information, color could be used to represent the demographic of the group. What if the information that are interesting lies in the times domain, how could the plot captured that information?

!!general sankey plot and sankey with color

The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer. Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time. The animation in this tools has created a new way for people to analyse and visualize the trend.

!!read effectiveness of animation in trend visualization, then add more information to above paragraph

The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world. This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.

@@

\bibliography{animbook-journal.bib}
